---
title: ""
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

## Overview

The package creates a new `Geom`, `geom_design`, which can be used alongside `ggplot2` to depict experimental designs. Note that all the usual `ggplot` machinery can be used. 

### Installation

```{r, eval = FALSE}
devtools::install_github("cmjt/ggdesign")
```

## Using `geom_design()`

Below are some options showing how you might plot some well known designs. The `R` package `agricolae` is used to simulate the different designs.

```{r}
library(ggplot2)
library(ggdesign)
library(agricolae)
```


### Completely Randomised Design (CRD)

```{r}
set.seed(1642)
trt <- c("A", "B", "C")
crd <- agricolae::design.crd(trt = trt, r = 2)$book
crd
ggplot(crd, aes(plots = plots, fill = trt)) +
    geom_design()
```
 
#### We can change those default colours {-}

```{r}
ggplot(crd, aes(plots = plots, fill = trt)) +
    geom_design() + scale_fill_brewer(palette = "Dark2")
```

#### We can change the type of unit {-}

```{r}
ggplot(crd, aes(plots = plots, fill = trt)) +
    geom_design(type = "hex") + scale_fill_brewer(palette = "Dark2")
```

### Randomised Complete Block Design (RCBD)

```{r}
set.seed(1647)
trt <- c("A", "B", "C")
rcbd <- agricolae::design.rcbd(trt = trt, r = 3)$book
rcbd
```
```{r}
ggplot(rcbd, aes(plots = plots, fill = trt, block = block)) +
    geom_design() + scale_fill_brewer(palette = "Dark2")
```

### Factorial Design

```{r}
set.seed(7861)
fact <- agricolae::design.ab(trt = c(3, 2), r = 2, design = "crd")$book
fact
```

```{r}
ggplot(fact, aes(plots = plots, fill = A, col = B, block = r)) +
    geom_design(type = "hex") + scale_fill_brewer(palette = "Dark2")
```

### Split-plot Design 

```{r}
set.seed(8881)
## split plot
trt1 <- c("A", "B"); trt2 <- LETTERS[1:4]
sp <- agricolae::design.split(trt1 = trt1, trt2 = trt2, r = 2, design = "crd")$book
```

#### Using colour for the second treatment {-}

```{r}
ggplot(sp, aes(plots = plots, fill = trt1, block = splots, col = trt2)) +
    geom_design()
```

#### Or a different unit shape... {-}

```{r}
ggplot(sp, aes(plots = plots, fill = trt1, block = splots)) +
    geom_design(type = "hex_tri") +
    geom_design(aes(fill = trt2), type = "hex_tri", seg = 2) +
    scale_fill_brewer(palette = "Paired")
```

## Working on ANOVA tables...
